### 2020-04-21 final_report/results.tex
Added bibliography .bib file
add supervised learning result intro

>>>>

We begin by evaluating a diverse set of surrogate classes that we proposed
earlier. In particular, we aim to study considered models in terms of regression
performance and evaluation complexity.
Following~\cref{sec:experiment-methodology}, where we proposed four experiments
that accomplish this task, we present and discuss our results in the following
sections.
